A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-02 tex/codatadp.tex
more

* although nothing prevents composing the decision procedure with theories
  providing polymorphic types (parametric sorts), such as for arrays (e.g., \ty{array}(\alpha,\beta))

@@

We assume a signature $\Sigma = (\mathcal{T}, \mathcal{F})$.
Furthermore, a partition of the types:
  $\mathcal{T} = \mathcal{I} \uplus \mathcal{C} \uplus \mathcal{N}$
with
  * $\mathcal{I}$: datatypes
  * $\mathcal{C}$: codatatypes
  * $\mathcal{N}$: non-(co)datatypes

>>>>

* although nothing prevents composing the decision procedure with theories
  providing polymorphic types (parametric sorts), such as for arrays (e.g., $\ty{array}(\alpha,\beta)$)

@@

We assume a signature $\Sigma = (\mathcal{T}, \mathcal{F})$.

Furthermore, a partition of the types:
  $\mathcal{T} = \mathcal{I} \uplus \mathcal{C} \uplus \mathcal{N}$
with
  * $\mathcal{D}$: datatypes
  * $\mathcal{C}$: codatatypes
  * $\mathcal{N}$: non-(co)datatypes

And a partition of the functions:
  * $\mathcal{C}$

for each datatype or codatatype $\delta$:
  *
